Structuring College Access

### 2025-02-21 index.qmd
final sea presentationgit add .

### New York and Chicago Geomarkets {.hide}

@@

<p class="quote">Geomarkets</p>
<p style="display:none;">Boundaries [often] match formal political and educational divisions, reflecting natural channels of communication. Each major metro area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs [@RN4982, p. 4].</p>

@@

- Census tract-level data
  - 1980, 2000 Census; 2016-2020 American Community Survey (ACS)
- Geomarket shapefiles obtained from a 2012 blog post
  - Each zip code assigned to one Geomarket
- Partial spatial assigns each Census tract to one or more Geomarkets

@@

- Hasn't examined quantification that classifies consumers for producers
  - Structural inequality $\rightarrow$ unequal student demand for college
  - College access structured by third-party products that encourage supply-side to amplify structural inequalities observed on demand-side
- @RN5005 show effect of quantification, but not mechanisms of *how* quantification produces inequality

>>>>

### Geomarkets around Chicago-land {.hide}

@@

<p class="quote">Geomarkets</p>
<p style="display:none;">Boundaries [often] match formal political and educational divisions, reflecting natural channels of communication. **Each major metro area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs.** In more sparsely populated areas, communities are sometimes combined in order to make the analysis meaningful. [@RN4982, p. 4].</p>

@@

- Census tract-level data
  - 1980, 2000 Census, 2016-2020 American Community Survey (ACS)
- Geomarket shapefiles obtained from a 2012 blog post
  - Each zip code assigned to one Geomarket
- Partial spatial assigns each Census tract to one or more Geomarkets

@@

- Hasn't examined quantification that classifies consumers for producers
  - Structural inequality $\rightarrow$ unequal student demand for college
  - Third-party products take snapshot student demand $\rightarrow$ encourage supply-side to amplify structural inequalities observed on demand-side
- @RN5005 show effect of quantification, but not mechanisms of *how* quantification produces inequality
